Downward shortwave solar irradiance enhancement by clouds.

### 2024-05-26 article/article.Rmd
Commit 2024-05-26 16:14

author:
  - name:        Athanasios N. Natsis
    email:       natsisphysicist@gmail.com
    affiliation: LAP
    correspondingauthor: true
    footnote: 1
  - name:        Alkiviadis Bais
    email:       abais@auth.gr
    affiliation: LAP
  - name:        Charikleia Meleti
    email:       meleti@auth.gr
    affiliation: LAP
    footnote: 2
address:
  - code:         LAP
    organization: Laboratory of Atmospheric Physics, A.U.Th.
    addressline:  1 main street
    city:         Thessaloniki
    postcode:     123456
    country:      Greece
  - code:         Another University
    organization: Department
    addressline:  A street 29
    postcode:     2054 NX
    city:         Manchester,
    state:        State
    country:      The Netherlands
footnote:
  - code: 1
    text: "This is the first author footnote."
  - code: 2
    text: "Another author footnote."
abstract: |
  Here wii be the abstract.

@@

keywords: 
  - keyword1
  - keyword2

@@

We computed the daily trend of the mean OIR of CE <!--
(Figure\nobreakspace{}\ref{fig:CEmeanDaily}), --> using a first-order autoregressive
model with a lag of one day, with the 'maximum likelihood' fitting method
[@Gardner1980; @Jones1980] by implementing the function 'arima' from the library
'stats' of the R programming language [@RCT2023]. The trends are reported together
with the $2\sigma$ error.  We observed a negligible change of
$`r round(dailyCE[var == "GLB_diff.mean", Tmod_Estimate], 3)`\pm
`r round(2 * dailyCE[var == "GLB_diff.mean", Tmod_Std..Error], 3)`\,W/m^2/y$
on the mean OIR.
<!-- ```{r CEmeanDaily, echo=FALSE, fig.cap="Daily mean values and trend of the CE over irradiance."} -->
<!-- knitr::include_graphics("../images/P_daily_trend-1.png") -->
<!-- ``` -->
Although, the previous result is closer to the raw data, we preferred to present the
annual statistics, that give a more clear picture about the long term CE trends.
Hence, we calculated the annual values from the one-minute measurements.  Despite the
very weak statistical significance of the mean OIR trend, the annual number of CE
occurrences shows a steady increase of
$`r round(yearlyCE[var == "GLB_diff.N", slope], 1)`\pm
`r round(2 * yearlyCE[var == "GLB_diff.N", slope.sd], 1)`\,\text{cases}/\text{year}$
(Figure\nobreakspace{}\ref{fig:P-energy-N}).
Subsequently, the mean annual energy of the CE events is increasing with a rate of
$`r round(yearlyCE[var == "GLB_diff.sum", slope], 1)`\pm
`r round(2 * yearlyCE[var == "GLB_diff.sum", slope.sd], 1)`\,\text{kj}/\text{year}$
(Figure\ \ref{fig:P-energy-sum}), witch follows the trend of the number of CE
occurrences.  We have to note that the energy related to the CE events can not be
directly linked with the total energy balance of the atmosphere. The net solar
radiation of the region is not increased, but rather redistributed through the CE
events.  This also is depicted by the "instantaneous" values of irradiance (average
over one minute), that can exceed the equivalent clear sky irradiance to a
considerable level.

@@

The distribution of the CE over irradiance intensity follows an exponential decline
Figure\nobreakspace{}\ref{fig:ovir-distribution}, where there is an inverse relation
between the events frequency and events intensity. This is expected as, the stronger
the CE events become, the rarer the particular atmospheric and sun conditions will
occur. This is indicative to the magnitude and probability of the expected OIRs
events over Thessaloniki.

@@

```{r echo=FALSE, fig.cap="Distribution of ECE above clear sky threshold."}
knitr::include_graphics("../images/P-extreme-distribution-1.png")
```

@@

The magnitude of the ECE events doesn't exceeds the values reported from sites with
more favorable conditions for the phenomenon. Although, the climatological
characteristic of the ECE events, showed that the most active months are spread on
half of the year (March -- June and September and October).

We find that CE conditions can have a duration of more than an hour in rare
cases, with the bulk of the cases having a duration under 5 minutes.

Our find have similarities with other mediterranean / europe sites.

@@

Compare to other location stats.
max, ECE, distributions ....

>>>>

author:
  - name:        Athanasios N. Natsis
    email:       natsisphysicist@gmail.com
    affiliation: LAP
    correspondingauthor: true
    footnote: 1
  - name:        Alkiviadis Bais
    email:       abais@auth.gr
    affiliation: LAP
  - name:        Charikleia Meleti
    email:       meleti@auth.gr
    affiliation: LAP
    footnote: 2
address:
  - code:         LAP
    organization: Laboratory of Atmospheric Physics, Physics Department, Aristotle University of Thessaloniki
    # addressline:  1 main street
    city:         Thessaloniki
    postcode:     54124
    country:      Greece
  - code:         Another University
    organization: Department
    addressline:  A street 29
    postcode:     2054 NX
    city:         Manchester,
    state:        State
    country:      The Netherlands
footnote:
  - code: 1
    text: "This is the first author footnote."
  - code: 2
    text: "Another author footnote."
abstract: |
  Here wii be the abstract.

@@

keywords: 
  - cloud enhancement
  - total solar radiation
  - global horizonta irradiance
  - over irradiance

@@

We computed the daily trend of the mean OIR of CE <!--
(Figure\nobreakspace{}\ref{fig:CEmeanDaily}), --> using a first-order autoregressive
model with a lag of one day, with the 'maximum likelihood' fitting method
[@Gardner1980; @Jones1980] by implementing the function 'arima' from the library
'stats' of the R programming language [@RCT2023]. The trends are reported together
with the $2\sigma$ error.  We observed a negligible change of
$`r round(dailyCE[var == "GLB_diff.mean", Tmod_Estimate], 3)`\pm
`r round(2 * dailyCE[var == "GLB_diff.mean", Tmod_Std..Error], 3)`\,\text{W}/\text{m}^2/\text{year}$
on the mean OIR.
<!-- ```{r CEmeanDaily, echo=FALSE, fig.cap="Daily mean values and trend of the CE over irradiance."} -->
<!-- knitr::include_graphics("../images/P_daily_trend-1.png") -->
<!-- ``` -->
Although, the previous result is closer to the raw data, we preferred to present the
annual statistics, that give a more clear picture about the long term CE trends.
Hence, we calculated the annual values from the one-minute measurements.  Despite the
very weak statistical significance of the mean OIR trend, the annual number of CE
occurrences shows a steady increase of
$`r round(yearlyCE[var == "GLB_diff.N", slope], 1)`\pm
`r round(2 * yearlyCE[var == "GLB_diff.N", slope.sd], 1)`\,\text{cases}/\text{year}$
(Figure\nobreakspace{}\ref{fig:P-energy-N}).
Subsequently, the mean annual energy of the CE events is increasing with a rate of
$`r round(yearlyCE[var == "GLB_diff.sum", slope], 1)`\pm
`r round(2 * yearlyCE[var == "GLB_diff.sum", slope.sd], 1)`\,\text{kj}/\text{year}$
(Figure\ \ref{fig:P-energy-sum}), witch follows the trend of the number of CE
occurrences.  We have to note that the energy related to the CE events can not be
directly linked with the total energy balance of the atmosphere. The net solar
radiation of the region is not increased, but rather redistributed through the CE
events.  This also is depicted by the "instantaneous" values of irradiance (average
over one minute), that can exceed the equivalent clear sky irradiance to a
considerable level.

@@

The distribution of the CE over irradiance intensity follows an exponential decline
Figure\nobreakspace{}\ref{fig:ovir-distribution}, where there is an inverse relation
between the events frequency and events intensity. This is expected as, the stronger
the CE events become, the rarer the particular atmospheric and sun conditions will
occur. This fact is indicative to the magnitude and probability of the expected OIRs
events over Thessaloniki. Similar distribution of CE occurrences have been reported
by @Vamvakas2020, where the magnitude of OIR is 
higher due to the location of the the city of Patras, $2.5^\circ$ closer to the equator.

@@

The distribution of the ECE events (Figure\nobreakspace{}\ref{fig:P-extreme-distribution}), shows that there are rare cases where the OIR can exceed the 
TSI even more than $400\,\text{W}/\text{m}^2$, with the $75\,\%$ of the cases to be below $200\,\text{W}/\text{m}^2$. Similar to CE cases, the  distribution of ECE have a similar pattern
with the results of @Vamvakas2020, with the difference that the OIR values are lower fro Thessaloniki.

```{r P-extreme-distribution, echo=FALSE, fig.cap="Distribution of ECE above clear sky threshold, for cases that are exceeding the TSI."}
knitr::include_graphics("../images/P-extreme-distribution-1.png")
```

@@

The magnitude of the ECE events doesn't exceeds the values reported from sites with
more favourable conditions for the phenomenon. Although, the climatological
characteristic of the ECE events, showed that the most active months are spread on
half of the year (March -- June and September and October).
We found that CE conditions, can have a duration of more than an hour in rare
cases, with the bulk of the cases having a duration under 5 minutes.
Some of the characteristics of CE and ECE events we analysed,
have strong similarities with results
by @Vamvakas2020, for a city southern of Thessaloniki, with analogues differences, due to the 
 higher intensity of the solar radiation.

@@

### 2024-05-26 article/article.tex
Commit 2024-05-26 16:14

  \title{Downward shortwave solar irradiance enhancement by clouds.}
    \author[LAP]{Athanasios N. Natsis%
  \corref{cor1}%
  \fnref{1}}
   \ead{natsisphysicist@gmail.com} 
    \author[LAP]{Alkiviadis Bais%
  %
  }
   \ead{abais@auth.gr} 
    \author[LAP]{Charikleia Meleti%
  %
  \fnref{2}}
   \ead{meleti@auth.gr} 
      \affiliation[LAP]{
    organization={Laboratory of Atmospheric Physics,
A.U.Th.},addressline={1 main
street},city={Thessaloniki},postcode={123456},country={Greece},}
    \affiliation[Another University]{
    organization={Department},addressline={A street
29},city={Manchester,},postcode={2054 NX},state={State},country={The
Netherlands},}
    \cortext[cor1]{Corresponding author}
    \fntext[1]{This is the first author footnote.}
    \fntext[2]{Another author footnote.}

@@

  It consists of two paragraphs.
  \end{abstract}
    \begin{keyword}
    keyword1 \sep 
    keyword2
  \end{keyword}

@@

We computed the daily trend of the mean OIR of CE using a first-order
autoregressive model with a lag of one day, with the `maximum
likelihood' fitting method \citep{Gardner1980, Jones1980} by
implementing the function `arima' from the library `stats' of the R
programming language \citep{RCT2023}. The trends are reported together
with the \(2\sigma\) error. We observed a negligible change of
\(0.087\pm 0.08\,W/m^2/y\) on the mean OIR. Although, the previous
result is closer to the raw data, we preferred to present the annual
statistics, that give a more clear picture about the long term CE
trends. Hence, we calculated the annual values from the one-minute
measurements. Despite the very weak statistical significance of the mean
OIR trend, the annual number of CE occurrences shows a steady increase
of \(45.6\pm 21.9\,\text{cases}/\text{year}\)
(Figure\nobreakspace{}\ref{fig:P-energy-N}). Subsequently, the mean
annual energy of the CE events is increasing with a rate of
\(116.9\pm 67.8\,\text{kj}/\text{year}\)
(Figure~\ref{fig:P-energy-sum}), witch follows the trend of the number
of CE occurrences. We have to note that the energy related to the CE
events can not be directly linked with the total energy balance of the
atmosphere. The net solar radiation of the region is not increased, but
rather redistributed through the CE events. This also is depicted by the
``instantaneous'' values of irradiance (average over one minute), that
can exceed the equivalent clear sky irradiance to a considerable level.

@@

The distribution of the CE over irradiance intensity follows an
exponential decline Figure\nobreakspace{}\ref{fig:ovir-distribution},
where there is an inverse relation between the events frequency and
events intensity. This is expected as, the stronger the CE events
become, the rarer the particular atmospheric and sun conditions will
occur. This is indicative to the magnitude and probability of the
expected OIRs events over Thessaloniki.

@@

@@

\caption{Distribution of ECE above clear sky threshold.}\label{fig:unnamed-chunk-3}
\end{figure}

@@

The magnitude of the ECE events doesn't exceeds the values reported from
sites with more favorable conditions for the phenomenon. Although, the
climatological characteristic of the ECE events, showed that the most
active months are spread on half of the year (March -- June and
September and October).

We find that CE conditions can have a duration of more than an hour in
rare cases, with the bulk of the cases having a duration under 5
minutes.

Our find have similarities with other mediterranean / europe sites.

@@

Compare to other location stats. max, ECE, distributions \ldots.

>>>>

  \title{Downward shortwave solar irradiance enhancement by clouds.}
    \author[LAP]{Athanasios N. Natsis%
  \corref{cor1}%
  \fnref{1}}
   \ead{natsisphysicist@gmail.com} 
    \author[LAP]{Alkiviadis Bais%
  %
  }
   \ead{abais@auth.gr} 
    \author[LAP]{Charikleia Meleti%
  %
  \fnref{2}}
   \ead{meleti@auth.gr} 
      \affiliation[LAP]{
    organization={Laboratory of Atmospheric Physics, Physics Department,
Aristotle University of
Thessaloniki},city={Thessaloniki},postcode={54124},country={Greece},}
    \affiliation[Another University]{
    organization={Department},addressline={A street
29},city={Manchester,},postcode={2054 NX},state={State},country={The
Netherlands},}
    \cortext[cor1]{Corresponding author}
    \fntext[1]{This is the first author footnote.}
    \fntext[2]{Another author footnote.}

@@

  It consists of two paragraphs.
  \end{abstract}
    \begin{keyword}
    cloud enhancement \sep total solar radiation \sep global horizonta
irradiance \sep 
    over irradiance
  \end{keyword}

@@

We computed the daily trend of the mean OIR of CE using a first-order
autoregressive model with a lag of one day, with the `maximum
likelihood' fitting method \citep{Gardner1980, Jones1980} by
implementing the function `arima' from the library `stats' of the R
programming language \citep{RCT2023}. The trends are reported together
with the \(2\sigma\) error. We observed a negligible change of
\(0.087\pm 0.08\,\text{W}/\text{m}^2/\text{year}\) on the mean OIR.
Although, the previous result is closer to the raw data, we preferred to
present the annual statistics, that give a more clear picture about the
long term CE trends. Hence, we calculated the annual values from the
one-minute measurements. Despite the very weak statistical significance
of the mean OIR trend, the annual number of CE occurrences shows a
steady increase of \(45.6\pm 21.9\,\text{cases}/\text{year}\)
(Figure\nobreakspace{}\ref{fig:P-energy-N}). Subsequently, the mean
annual energy of the CE events is increasing with a rate of
\(116.9\pm 67.8\,\text{kj}/\text{year}\)
(Figure~\ref{fig:P-energy-sum}), witch follows the trend of the number
of CE occurrences. We have to note that the energy related to the CE
events can not be directly linked with the total energy balance of the
atmosphere. The net solar radiation of the region is not increased, but
rather redistributed through the CE events. This also is depicted by the
``instantaneous'' values of irradiance (average over one minute), that
can exceed the equivalent clear sky irradiance to a considerable level.

@@

The distribution of the CE over irradiance intensity follows an
exponential decline Figure\nobreakspace{}\ref{fig:ovir-distribution},
where there is an inverse relation between the events frequency and
events intensity. This is expected as, the stronger the CE events
become, the rarer the particular atmospheric and sun conditions will
occur. This fact is indicative to the magnitude and probability of the
expected OIRs events over Thessaloniki. Similar distribution of CE
occurrences have been reported by \citet{Vamvakas2020}, where the
magnitude of OIR is higher due to the location of the the city of
Patras, \(2.5^\circ\) closer to the equator.

@@

The distribution of the ECE events
(Figure\nobreakspace{}\ref{fig:P-extreme-distribution}), shows that
there are rare cases where the OIR can exceed the TSI even more than
\(400\,\text{W}/\text{m}^2\), with the \(75\,\%\) of the cases to be
below \(200\,\text{W}/\text{m}^2\). Similar to CE cases, the
distribution of ECE have a similar pattern with the results of
\citet{Vamvakas2020}, with the difference that the OIR values are lower
fro Thessaloniki.

@@

\caption{Distribution of ECE above clear sky threshold, for cases that are exceeding the TSI.}\label{fig:P-extreme-distribution}
\end{figure}

@@

The magnitude of the ECE events doesn't exceeds the values reported from
sites with more favourable conditions for the phenomenon. Although, the
climatological characteristic of the ECE events, showed that the most
active months are spread on half of the year (March -- June and
September and October). We found that CE conditions, can have a duration
of more than an hour in rare cases, with the bulk of the cases having a
duration under 5 minutes. Some of the characteristics of CE and ECE
events we analysed, have strong similarities with results by
\citet{Vamvakas2020}, for a city southern of Thessaloniki, with
analogues differences, due to the higher intensity of the solar
radiation.

@@
